# Data import

## interactive with Operation System[OS]
get current working loaction:
```{python}
import os 
print(os.getcwd())
```

Set current working loaction:
```{python eval=FALSE}
import os
os.chdir("C:\\Users\\tduan\\Desktop\\Mission\\R\\R_code\\Get_Python\\Book")
```

Get computer info:
```{python}
import platform
print(platform.machine())
print(platform.platform())
print(platform.system())
print(platform.processor())
print(platform.python_version())
```

Get file size:
```{r eval=FALSE}
#install.packages('pryr')
library(pryr)
object_size(mtcars)
```

Check how much memory R is using :
```{r eval=FALSE}
mem_used()
memory.size()
```

Check RAM limit :
```{r warning=FALSE}
memory.limit()
```

Show location files:
```{python}
import os
print(os.listdir())
```


Open ebay.com with firefox:


Open ebay.com with defalt browser:


Delete a file with unlink or file.remove():


Check a file existence:


Create a folder :


Delete a folder :


Download Files:


Zip A.txt and B.txt into A_B.zip:


Unzip A_B.zip



Untar a file:


Check file info:



Shutdown Computer in 10 seconds:



## Play music


## image


## txt 



## CSV
Read csv file:
```{python eval=FALSE}
import pandas as pd
df_csv = pd.read_csv('zipcode.csv')
print(df_csv.head())
```

Create csv file:
```{python eval=FALSE}
import pandas as pd
df_csv = pd.read_csv('zipcode.csv')
df_csv.to_csv('python_out_csv.csv', sep='\t')
```


## Excel

### xlsx Package

Read Excel file:
```{python eval=FALSE}
import pandas as pd
xl = pd.ExcelFile('df.xlsx')
print(xl.sheet_names)
# Load a sheet into a DataFrame by name: df1
df1 = xl.parse('data_sheet1')
print(df1.head())
# Load a sheet into a DataFrame by index: df2
df2 = xl.parse(0)
```

Create Excel file:
```{python eval=FALSE}
import pandas as pd
#  import
xl = pd.ExcelFile('df.xlsx')
print(xl.sheet_names)
# Load a sheet into a DataFrame by name: df1
df1 = xl.parse('data_sheet1')

#  export
writer = pd.ExcelWriter('python_out_excel.xlsx')
df1.to_excel(writer,'Sheet1')
```



## Google sheet
https://www.youtube.com/watch?v=7l2_R61jrUU&list=PLH6mU1kedUy-IW8mi46ZhowTm3-_yQNAQ

## Database 
sqlalchemy package
```{python eval=FALSE}
# Import necessary module
import pandas as pd
from sqlalchemy import create_engine

# Create engine: engine
engine = create_engine('sqlite:///Chinook.sqlite')

# Save the table names to a list: table_names
table_names = engine.table_names()

# Print the table names to the shell
print(table_names)

# Open engine connection
con = engine.connect()

# Perform query: rs
rs = con.execute("SELECT * FROM Album")

# Save results of the query to DataFrame: df
df = pd.DataFrame(rs.fetchall())
print(df.head())
```



## SAS SPSS Stata Matlab
```{python eval=FALSE}


# SAS
import pandas as pd
from sas7bdat import SAS7BDAT

# Save file to a DataFrame: df_sas
with SAS7BDAT('airline.sas7bdat') as file:
    df_sas = file.to_data_frame()

# Print head of DataFrame
print(df_sas.head())


# SPSS


# Stata
df_stata = pd.read_stata('alcohol.dta')
print(df_stata.head())

# matlab

```

## HTTP
Coming soon

## API & JSON
Coming soon

## Web Crawler
More on Get_Graphic & web_crawler




