# Data import

## interactive with Operation System[OS]
get current working loaction:
```{python}
import os 
print(os.getcwd())
```

Set current working loaction:
```{python}
import os
os.chdir("C:\\Users\\tduan\\Desktop\\Mission\\R\\R_code\\Get_Python\\Book")
```

Get computer info:
```{python}
import platform
print(platform.machine())
print(platform.platform())
print(platform.system())
print(platform.processor())
print(platform.python_version())
```

Get file size:
```{r eval=FALSE}
#install.packages('pryr')
library(pryr)
object_size(mtcars)
```

Check how much memory R is using :
```{r eval=FALSE}
mem_used()
memory.size()
```

Check RAM limit :
```{r warning=FALSE}
memory.limit()
```

Show location files:
```{python}
import os
print(os.listdir())
```


Open ebay.com with firefox:


Open ebay.com with defalt browser:


Delete a file with unlink or file.remove():


Check a file existence:


Create a folder :


Delete a folder :


Download Files:


Zip A.txt and B.txt into A_B.zip:


Unzip A_B.zip



Untar a file:


Check file info:



Shutdown Computer in 10 seconds:



## Play music


## image


## txt 



## CSV
Read csv file:
```{python eval=FALSE}
import pandas as pd
xl = pd.ExcelFile('df.xlsx')
print(xl.sheet_names)
# Load a sheet into a DataFrame by name: df1
df1 = xl.parse('data_sheet1')
# Load a sheet into a DataFrame by index: df2
df2 = xl.parse(0)
```

Create csv file:
```{r eval=FALSE}
write.csv(txt_df, file = "txt_df_out.csv")
```


## Excel

### xlsx Package

Read Excel file:
```{r eval=FALSE}
library(xlsx)
excel_df1=read.xlsx("df.xlsx", sheetIndex =1)                          #read 1 sheets 
excel_df2=read.xlsx("df.xlsx", sheetIndex =1,startRow=2, colIndex = 2) #read 1 sheets start from 2 row and 2 colmun
```

Create Excel file:
```{r eval=FALSE}
library(xlsx)
write.xlsx(mtcars, 
           "df.xlsx", 
           sheetName="data_sheet1"
           )
```



## Google sheet
https://www.youtube.com/watch?v=7l2_R61jrUU&list=PLH6mU1kedUy-IW8mi46ZhowTm3-_yQNAQ

## Database 
Coming soon
RJDBC

dplyr


## SAS SPSS Stata Matlab
```{r eval=FALSE}
install.packages("haven")
library(haven)
# SAS
read_sas("mtcars.sas7bdat")
write_sas(mtcars, "mtcars.sas7bdat")

# SPSS
read_sav("mtcars.sav")
write_sav(mtcars, "mtcars.sav")

# Stata
read_dta("mtcars.dta")
write_dta(mtcars, "mtcars.dta")

# matlab
install.packages("R.matlab")
library(R.matlab)
readMat('file.mat'))
```

## HTTP
Coming soon

## API & JSON
Coming soon

## Web Crawler
More on Get_Graphic & web_crawler




