# Data EDA and Visualization

Some _significant_ applications are demonstrated in this chapter.





## Base data set
```{python eval=FALSE}
import seaborn.apionly as sns
iris = sns.load_dataset('iris')
iris.head()
```



## EDA
what ;who ;where;when how

who 
who genrate the data and who will use the data


where
where the data being genrate

when 


how




```{python warning=FALSE,message=FALSE}
iris.info()

iris.info.describe()
```


  
### Correlation
Correlation coefficent Between -1 and 1.  
Sign->direction and Magnitude->strength  

```{r eval=FALSE}
# Pearson product-moment correlation(r) with no missing value
library(tidyverse)
mtcars %>%summarize(N = n(), r = cor(mpg,wt, 
                                     use = "pairwise.complete.obs"))

mtcars %>%group_by(cyl)%>%summarize(N = n(), r = cor(mpg,wt, 
                                     use = "pairwise.complete.obs"))

```

### Simple linear regression

Scatterplot with regression line
```{r message=FALSE,warning=FALSE}
library(ggplot2)
ggplot(data = mtcars, aes(x = mpg, y = wt)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE)
```


## Visualization

###Matplotlib  

###bokeh  

### plotly


https://plot.ly/r/
```{r message=FALSE,warning=FALSE}
#install.packages("plotly")
library(plotly)
packageVersion('plotly')
```

Scatter chart

```{r message=FALSE,warning=FALSE}
p <- plot_ly(data = iris, x = ~Sepal.Length, y = ~Petal.Length, color = ~Species)
p
```

line chart

bar chart

histogram chart

pie chart(not important)

time servies chart


### Bokeh

http://hafen.github.io/rbokeh/#background


```{r message=FALSE,warning=FALSE}
#install.packages("rbokeh")
library(rbokeh)
```

Scatter chart
```{r message=FALSE,warning=FALSE}
p <- figure() %>%
  ly_points(Sepal.Length, Sepal.Width, data = iris,
            color = Species, glyph = Species,
            hover = list(Sepal.Length, Sepal.Width))
p
```
line chart

bar chart

histogram chart

pie chart(not important)

time servies chart



### Map



