# Data EDA and Visualization

Some _significant_ applications are demonstrated in this chapter.





## Base data set
```{r eval=FALSE}
library(help = "datasets")

?iris
?mtcars
```



## EDA
what ;who ;where;when how

who 
who genrate the data and who will use the data


where
where the data being genrate

when 


how




```{r warning=FALSE,message=FALSE}
library(dplyr)
head(iris)       # first 5 rows
head(iris,n=10)  # first 10 rows

tail(iris)       # last 5 rows

class(iris)      # object type
dim(iris)        # how many rows and how many columns

summary(iris)    # summary of the data
glimpse(iris)    # a another way to smmarize the data with dplyr
```


  
### Correlation
Correlation coefficent Between -1 and 1.  
Sign->direction and Magnitude->strength  

```{r eval=FALSE}
# Pearson product-moment correlation(r) with no missing value
library(tidyverse)
mtcars %>%summarize(N = n(), r = cor(mpg,wt, 
                                     use = "pairwise.complete.obs"))

mtcars %>%group_by(cyl)%>%summarize(N = n(), r = cor(mpg,wt, 
                                     use = "pairwise.complete.obs"))

```

### Simple linear regression

Scatterplot with regression line
```{r message=FALSE,warning=FALSE}
library(ggplot2)
ggplot(data = mtcars, aes(x = mpg, y = wt)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE)
```


## Visualization

A Chart means thousand words.a good infographic can tell a story in many ways 

More on Get_Graphic & web_crawler

### Base plot
histogram chart
```{r message=FALSE,warning=FALSE}
hist(mtcars$wt)
```

### ggplot

Grammar of graphic 

#### qplot
Scatter plot:
```{r message=FALSE,warning=FALSE}
library(ggplot2)
#Scatter
qplot(displ,hwy,data=mpg)
qplot(displ,hwy,data=mpg,color=drv)# group with color
qplot(displ,hwy,data=mpg,shape=drv)# group with shape
```

Scatter and line:
```{r warning=FALSE,message=FALSE}
library(ggplot2)
qplot(displ,hwy,data=mpg,geom=c('point','smooth'))
```

Histogram:
```{r message=FALSE,warning=FALSE}
qplot(hwy,data=mpg)
qplot(hwy,data=mpg,fill=drv)# group with color
```


facets
```{r message=FALSE,warning=FALSE}
qplot(displ,hwy,data=mpg,facets = .~drv)#facet
qplot(hwy,data=mpg,facets = .~drv,binwidth=2)# facet and binwidth setting
```

#### ggplot2

```{r message= FALSE, warning=FALSE}
library(ggplot2)
g=ggplot(mpg,aes(x=displ,y=hwy))
```

Scatter
```{r message=FALSE,warning=FALSE}
g+geom_point()
```

```{r message=FALSE,warning=FALSE}
g+geom_point()+facet_grid(.~ cyl)+geom_smooth(method='lm')
```


```{r message=FALSE,warning=FALSE}
g+geom_point(color='steelblue',size=4,alpha=0.5)

g+geom_point(aes(color=as.factor(cyl)),size=4,alpha=0.5)
```



bar chart

histogram chart

pie chart(not important)

time servies chart



http://tutorials.iq.harvard.edu/R/Rgraphics/Rgraphics.html

https://rpubs.com/g_jw/ggplot2_tutorial


### plotly


https://plot.ly/r/
```{r message=FALSE,warning=FALSE}
#install.packages("plotly")
library(plotly)
packageVersion('plotly')
```

Scatter chart

```{r message=FALSE,warning=FALSE}
p <- plot_ly(data = iris, x = ~Sepal.Length, y = ~Petal.Length, color = ~Species)
p
```

line chart

bar chart

histogram chart

pie chart(not important)

time servies chart


### Bokeh

http://hafen.github.io/rbokeh/#background


```{r message=FALSE,warning=FALSE}
#install.packages("rbokeh")
library(rbokeh)
```

Scatter chart
```{r message=FALSE,warning=FALSE}
p <- figure() %>%
  ly_points(Sepal.Length, Sepal.Width, data = iris,
            color = Species, glyph = Species,
            hover = list(Sepal.Length, Sepal.Width))
p
```
line chart

bar chart

histogram chart

pie chart(not important)

time servies chart



### Map



