# Data EDA and Visualization

Some _significant_ applications are demonstrated in this chapter.



dont let the datasad make your mind datasad

## Base data set
```{r eval=FALSE}
library(help = "datasets")
library(ggplot2)
?iris
?mtcars
?mpg
```


## EDA
what ;who ;where;when how

who 
who genrate the data and who will use the data


where
where the data being genrate

when 


how




```{r warning=FALSE,message=FALSE}
library(dplyr)
head(iris)       # first 5 rows
head(iris,n=10)  # first 10 rows

tail(iris)       # last 5 rows

class(iris)      # object type
dim(iris)        # how many rows and how many columns
str(iris)        # structure of the data
summary(iris)    # summary of the data
glimpse(iris)    # a another way to smmarize the data with dplyr
```


  
### Correlation
Correlation coefficent Between -1 and 1.  
Sign->direction and Magnitude->strength  

```{r eval=FALSE}
# Pearson product-moment correlation(r) with no missing value
library(tidyverse)
mtcars %>%summarize(N = n(), r = cor(mpg,wt, 
                                     use = "pairwise.complete.obs"))

mtcars %>%group_by(cyl)%>%summarize(N = n(), r = cor(mpg,wt, 
                                     use = "pairwise.complete.obs"))

```

### Simple linear regression

Scatterplot with regression line
```{r message=FALSE,warning=FALSE}
library(ggplot2)
ggplot(data = mtcars, aes(x = mpg, y = wt)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE)
```


## Visualization

A Chart means thousand words.a good infographic can tell a story in many ways 

More on Get_Graphic & web_crawler

### Basic plot
histogram chart
```{r message=FALSE,warning=FALSE}
hist(mtcars$wt)
```

### ggplot

Package ggplot is Grammar of graphic;

Top 50 ggplot2 Visualizations - The Master List:
http://r-statistics.co/Top50-Ggplot2-Visualizations-MasterList-R-Code.html
```{r message= FALSE, warning=FALSE}
library(ggplot2)
```


1. data
The dataset used to make the graphic.Better to use one dataset instead of multiple dataset  

2. aesthetic
variable in the dataset to make the graphic.In ggplot land aesthetic means 'something you can see'

3. geom
Geometric objects are the actual marks we put on a plot. Examples include:lines,points,boxplots ect.

4. coordinate

5. Facet

6. Scales

7. Stats

8. Labels
title,x label,y label

9. Legends

10. Themes


Graphic example:


#### Scatter:
scatter plot between cty and hwy color by manufacturer
```{r message= FALSE, warning=FALSE}
library(ggplot2)
f =ggplot(mpg, aes(cty, hwy,color = manufacturer))+geom_point()
f
```


#### Scatter with smooth line:
scatter plot between cty and hwy color by manufacturer
```{r message= FALSE, warning=FALSE}
library(ggplot2)
f =ggplot(mpg, aes(cty, hwy）)+geom_point()+geom_smooth(method = "lm")
f
```

#### Histogram chart:
histogram display hwy and add color by manufacturer
```{r message=FALSE,warning=FALSE}
library(ggplot2)
a=ggplot(mpg, aes(hwy,fill = manufacturer))+geom_histogram()
a
```



#### Dot plot color by  manufacturer:
```{r message=FALSE,warning=FALSE}
a=ggplot(mpg, aes(hwy,fill = manufacturer))+geom_dotplot(aes(fill = manufacturer))
a
```


#### Bar chart:
```{r message=FALSE,warning=FALSE}
b=ggplot(mpg,aes(x=trans))
b+geom_bar()
```

Add color by fl
```{r message=FALSE,warning=FALSE}
b+geom_bar(aes(fill = fl)) 
```



#### Scatter:

```{r message= FALSE, warning=FALSE}
library(ggplot2)
f <- ggplot(mpg, aes(cty, hwy))
```


Add geom_point
```{r message=FALSE,warning=FALSE}
f+geom_point() + 
  labs(title =" New title", x = "New x", y = "New y") #label title,x,y
```

Add geom_point with facet & geom_smooth
```{r message=FALSE,warning=FALSE}
f+geom_point()+facet_grid(.~ cyl)+geom_smooth(method='lm')
```

Add geom_point with color
```{r message=FALSE,warning=FALSE}
f+geom_point(color='steelblue',size=4,alpha=0.5)
```

Add geom_point with group by cyl with color
```{r message=FALSE,warning=FALSE}
f+geom_point(aes(color=as.factor(cyl)),size=4,alpha=0.5)
```

#### point and line:
```{r message=FALSE,warning=FALSE}
f+geom_point()+geom_smooth(model = lm)
```


#### Boxplot:

```{r message=FALSE,warning=FALSE}
g <- ggplot(mpg, aes(class, hwy))

```

```{r message=FALSE,warning=FALSE}
g + geom_boxplot()
```



#### time servies line

```{r message=FALSE,warning=FALSE}
j <- ggplot(economics, aes(date, unemploy))
j + geom_line()
```


#### facet 
```{r message=FALSE,warning=FALSE}
t <- ggplot(mpg, aes(cty, hwy)) + geom_point()
t + facet_grid(. ~ fl)#facet into columns
t + facet_grid( fl~.)#facet into rows
t + facet_grid(year ~ fl)#facet year into rows,fl to columns
```

#### Legends

#### Themes

#### Map
```{r message=FALSE,warning=FALSE}
data <- data.frame(murder = USArrests$Murder, state = tolower(rownames(USArrests)))
map <- map_data("state")
l <- ggplot(data, aes(fill = murder))
l + geom_map(aes(map_id = state), map = map) +
expand_limits(x = map$long, y = map$lat)
```



#### pie chart(not important)


http://tutorials.iq.harvard.edu/R/Rgraphics/Rgraphics.html

https://rpubs.com/g_jw/ggplot2_tutorial


### plotly
https://www.youtube.com/watch?v=v_kK5c0QUnU
https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf  


https://plot.ly/r/
```{r message=FALSE,warning=FALSE}
#install.packages("plotly")
library(plotly)
packageVersion('plotly')
```

Scatter chart

simple: 
```{r message=FALSE,warning=FALSE}
plot_ly(data=mtcars, x = ~wt , y =~mpg,mode='markers')
```

group by numeric:
```{r message=FALSE,warning=FALSE}
plot_ly(data=mtcars, x = ~wt , y =~mpg,mode='markers',color = ~cyl)
```

group by factor:
```{r message=FALSE,warning=FALSE}
plot_ly(data=mtcars, x = ~wt , y =~mpg,mode='markers',color = ~as.factor(cyl))
```

group by factor + hp as dot size: 
```{r message=FALSE,warning=FALSE}
plot_ly(data=mtcars, x = ~wt , y =~mpg,mode='markers',color = ~as.factor(cyl),size=~hp)
```

3D scatter:
```{r message=FALSE,warning=FALSE}
plot_ly(data=mtcars, x = ~wt , y =~mpg,z=~hp,type="scatter3d",mode='markers',color = ~as.factor(cyl))
```






line chart:

line:
```{r message=FALSE,warning=FALSE}
plot_ly(x=~time(airmiles),y=~airmiles,mode='lines')
```

Multi line chart:
```{r message=FALSE,warning=FALSE}
library(plotly)
library(tidyr)
library(dplyr)
data("EuStockMarkets")
stocks <- as.data.frame(EuStockMarkets) %>%
  gather(index, price) %>%
  mutate(time = rep(time(EuStockMarkets), 4))
plot_ly(stocks, x = ~time, y = ~price, color = ~index)
```


histogram:
```{r message=FALSE,warning=FALSE}
library(plotly)
plot_ly(x = ~precip, type = "histogram")
```

bar chart
pie chart(not important)

boxplot:
```{r message=FALSE,warning=FALSE}
plot_ly(iris, y = ~Petal.Length, color = ~Species, type = "box")
```

Map one:
```{r message=FALSE,warning=FALSE}
library(plotly)
# Create data frame
state_pop <- data.frame(State = state.abb, Pop = as.vector(state.x77[,1]))
# Create hover text
state_pop$hover <- with(state_pop, paste(State, '<br>', "Population:", Pop))
# Make state borders white
borders <- list(color = toRGB("black"))
# Set up some mapping options
map_options <- list(
  scope = 'usa',
  projection = list(type = 'USA'),
  showlakes = TRUE,
  lakecolor = toRGB('white')
)

  
plot_ly(state_pop, z = ~Pop, text = ~hover, locations = ~State, 
        type = 'choropleth', locationmode = 'USA-states', 
        color = ~Pop, colors = 'Reds', marker = list(line = borders)) %>%
  layout(title = 'US Population in 1975', geo = map_options)
```

Map two:
```{r message=FALSE,warning=FALSE}
library(plotly)
df <- read.csv("https://raw.githubusercontent.com/plotly/datasets/master/2011_us_ag_exports.csv")
df$hover <- with(df, paste(state, '<br>', "Beef", beef, "Dairy", dairy, "<br>",
                           "Fruits", total.fruits, "Veggies", total.veggies,
                           "<br>", "Wheat", wheat, "Corn", corn))
# give state boundaries a white border
l <- list(color = toRGB("white"), width = 2)
# specify some map projection/options
g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = toRGB('white')
)

p <- plot_geo(df, locationmode = 'USA-states') %>%
  add_trace(
    z = ~total.exports, text = ~hover, locations = ~code,
    color = ~total.exports, colors = 'Purples'
  ) %>%
  colorbar(title = "Millions USD") %>%
  layout(
    title = '2011 US Agriculture Exports by State<br>(Hover for breakdown)',
    geo = g
    
  )
p
```


ggplot to Plotly
```{r message=FALSE,warning=FALSE}
library(plotly)
library(ggplot2)
g=ggplot(mpg,aes(x=displ,y=hwy))+geom_point()

p=ggplotly(g)
p
```


### Bokeh

http://hafen.github.io/rbokeh/#background


```{r message=FALSE,warning=FALSE}
#install.packages("rbokeh")
library(rbokeh)
```

Scatter chart
```{r message=FALSE,warning=FALSE}
p <- figure() %>%
  ly_points(Sepal.Length, Sepal.Width, data = iris,
            color = Species, glyph = Species,
            hover = list(Sepal.Length, Sepal.Width))
p
```
line chart

bar chart

histogram chart

pie chart(not important)

time servies chart


### ggmap

### leaflet

### ggvis

### GoogleVis

### googleCharts


### lattice

histogram:
```{r message=FALSE,warning=FALSE}
# Load the lattice package
library(lattice)
# Create the histogram 
histogram(~ Ozone, data = airquality)
```

Scatter chart:
```{r message=FALSE,warning=FALSE}
# Load the lattice package
library(lattice)
# Create the scatter plot
xyplot(Ozone ~ Solar.R, data = airquality)
```





