# Data EDA

Some _significant_ applications are demonstrated in this chapter.





## Base data set
```{r eval=FALSE}
library(help = "datasets")

?iris
?mtcars
```



## EDA
what ;who ;where;when how

who 
who genrate the data and who will use the data


where
where the data being genrate

when 


how




```{r warning=FALSE,message=FALSE}
library(dplyr)
head(iris)       # first 5 rows
head(iris,n=10)  # first 10 rows

tail(iris)       # last 5 rows

class(iris)      # object type
dim(iris)        # how many rows and how many columns

summary(iris)    # summary of the data
glimpse(iris)    # a another way to smmarize the data with dplyr
```

## Visualization

A Chart means thousand words.a good infographic can tell a story in many ways 

More on Get_Graphic & web_crawler

### Base plot(not recommend)
histogram chart
```{r}
hist(mtcars$wt)
```

### ggplot
```{r message=FALSE}
#install.packages("ggplot2")
library(ggplot2)
```

Scatter chart
```{r message=FALSE}
library(ggplot2)
ggplot(mtcars,
       aes(x=mpg,
           y=wt,
           color=as.factor(am)))+
  geom_point()
```
  
  
line chart
```{r message=FALSE}
library(ggplot2)
ggplot(mtcars,
       aes(x=mpg,
           y=wt,
           color=as.factor(am)))+
  geom_point()+geom_smooth()
```




bar chart

histogram chart

pie chart(not important)

time servies chart



http://tutorials.iq.harvard.edu/R/Rgraphics/Rgraphics.html

https://rpubs.com/g_jw/ggplot2_tutorial

### plotly
https://plot.ly/r/
```{r eval=FALSE}
install.packages("plotly")
library(plotly)
```

Scatter chart




line chart

bar chart

histogram chart

pie chart(not important)

time servies chart


### Bokeh
http://hafen.github.io/rbokeh/#background

```{r eval=FALSE}
install.packages("rbokeh")
library(rbokeh)
```

Scatter chart

line chart

bar chart

histogram chart

pie chart(not important)

time servies chart

  
## Correlation
Correlation coefficent Between -1 and 1.  
Sign->direction and Magnitude->strength  

```{r eval=FALSE}
# Pearson product-moment correlation(r) with no missing value
library(tidyverse)
mtcars %>%summarize(N = n(), r = cor(mpg,wt, 
                                     use = "pairwise.complete.obs"))

mtcars %>%group_by(cyl)%>%summarize(N = n(), r = cor(mpg,wt, 
                                     use = "pairwise.complete.obs"))

```

##Simple linear regression

Scatterplot with regression line
```{r}
library(ggplot2)
ggplot(data = mtcars, aes(x = mpg, y = wt)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE)
```









