# Data EDA and Visualization

Some _significant_ applications are demonstrated in this chapter.



dont let the datasad make your mind datasad

## Base data set
```{r eval=FALSE}
library(help = "datasets")

?iris
?mtcars
```



## EDA
what ;who ;where;when how

who 
who genrate the data and who will use the data


where
where the data being genrate

when 


how




```{r warning=FALSE,message=FALSE}
library(dplyr)
head(iris)       # first 5 rows
head(iris,n=10)  # first 10 rows

tail(iris)       # last 5 rows

class(iris)      # object type
dim(iris)        # how many rows and how many columns
str(iris)        # structure of the data
summary(iris)    # summary of the data
glimpse(iris)    # a another way to smmarize the data with dplyr
```


  
### Correlation
Correlation coefficent Between -1 and 1.  
Sign->direction and Magnitude->strength  

```{r eval=FALSE}
# Pearson product-moment correlation(r) with no missing value
library(tidyverse)
mtcars %>%summarize(N = n(), r = cor(mpg,wt, 
                                     use = "pairwise.complete.obs"))

mtcars %>%group_by(cyl)%>%summarize(N = n(), r = cor(mpg,wt, 
                                     use = "pairwise.complete.obs"))

```

### Simple linear regression

Scatterplot with regression line
```{r message=FALSE,warning=FALSE}
library(ggplot2)
ggplot(data = mtcars, aes(x = mpg, y = wt)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE)
```


## Visualization

A Chart means thousand words.a good infographic can tell a story in many ways 

More on Get_Graphic & web_crawler

### Basic plot
histogram chart
```{r message=FALSE,warning=FALSE}
hist(mtcars$wt)
```

### ggplot

Grammar of graphic 

#### qplot()
Scatter plot:
```{r message=FALSE,warning=FALSE}
library(ggplot2)
#Scatter
qplot(displ,hwy,data=mpg)
qplot(displ,hwy,data=mpg,color=drv)# group with color
qplot(displ,hwy,data=mpg,shape=drv)# group with shape
```

Scatter and line:
```{r warning=FALSE,message=FALSE}
library(ggplot2)
qplot(displ,hwy,data=mpg,geom=c('point','smooth'))
```

Histogram:
```{r message=FALSE,warning=FALSE}
qplot(hwy,data=mpg)
qplot(hwy,data=mpg,fill=drv)# group with color
```


facets
```{r message=FALSE,warning=FALSE}
qplot(displ,hwy,data=mpg,facets = .~drv)#facet
qplot(hwy,data=mpg,facets = .~drv,binwidth=2)# facet and binwidth setting
```

#### ggplot()

```{r message= FALSE, warning=FALSE}
library(ggplot2)
g=ggplot(mpg,aes(x=displ,y=hwy))
```

Scatter
```{r message=FALSE,warning=FALSE}
g=ggplot(mpg,aes(x=displ,y=hwy))
g+geom_point()
```

```{r message=FALSE,warning=FALSE}
g+geom_point()+facet_grid(.~ cyl)+geom_smooth(method='lm')
```


```{r message=FALSE,warning=FALSE}
g+geom_point(color='steelblue',size=4,alpha=0.5)

g+geom_point(aes(color=as.factor(cyl)),size=4,alpha=0.5)
```



bar chart

histogram chart

pie chart(not important)

time servies chart

Map





http://tutorials.iq.harvard.edu/R/Rgraphics/Rgraphics.html

https://rpubs.com/g_jw/ggplot2_tutorial


### plotly
https://www.youtube.com/watch?v=v_kK5c0QUnU
https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf  


https://plot.ly/r/
```{r message=FALSE,warning=FALSE}
#install.packages("plotly")
library(plotly)
packageVersion('plotly')
```

Scatter chart

simple: 
```{r message=FALSE,warning=FALSE}
plot_ly(data=mtcars, x = ~wt , y =~mpg,mode='markers')
```

group by numeric:
```{r message=FALSE,warning=FALSE}
plot_ly(data=mtcars, x = ~wt , y =~mpg,mode='markers',color = ~cyl)
```

group by factor:
```{r message=FALSE,warning=FALSE}
plot_ly(data=mtcars, x = ~wt , y =~mpg,mode='markers',color = ~as.factor(cyl))
```

group by factor + hp as dot size: 
```{r message=FALSE,warning=FALSE}
plot_ly(data=mtcars, x = ~wt , y =~mpg,mode='markers',color = ~as.factor(cyl),size=~hp)
```

3D scatter:
```{r message=FALSE,warning=FALSE}
plot_ly(data=mtcars, x = ~wt , y =~mpg,z=~hp,type="scatter3d",mode='markers',color = ~as.factor(cyl))
```






line chart-time servies

line:
```{r message=FALSE,warning=FALSE}
plot_ly(x=~time(airmiles),y=~airmiles,mode='lines')
```

Multi Line Graph:
```{r message=FALSE,warning=FALSE}
library(plotly)
library(tidyr)
library(dplyr)
data("EuStockMarkets")
stocks <- as.data.frame(EuStockMarkets) %>%
  gather(index, price) %>%
  mutate(time = rep(time(EuStockMarkets), 4))
plot_ly(stocks, x = ~time, y = ~price, color = ~index)
```


histogram:
```{r message=FALSE,warning=FALSE}
library(plotly)
plot_ly(x = ~precip, type = "histogram")
```

bar chart
pie chart(not important)

boxplot:
```{r message=FALSE,warning=FALSE}
plot_ly(iris, y = ~Petal.Length, color = ~Species, type = "box")
```

Map one:
```{r message=FALSE,warning=FALSE}
library(plotly)
# Create data frame
state_pop <- data.frame(State = state.abb, Pop = as.vector(state.x77[,1]))
# Create hover text
state_pop$hover <- with(state_pop, paste(State, '<br>', "Population:", Pop))
# Make state borders white
borders <- list(color = toRGB("black"))
# Set up some mapping options
map_options <- list(
  scope = 'usa',
  projection = list(type = 'USA'),
  showlakes = TRUE,
  lakecolor = toRGB('white')
)

  
plot_ly(state_pop, z = ~Pop, text = ~hover, locations = ~State, 
        type = 'choropleth', locationmode = 'USA-states', 
        color = ~Pop, colors = 'Reds', marker = list(line = borders)) %>%
  layout(title = 'US Population in 1975', geo = map_options)
```

Map two:
```{r message=FALSE,warning=FALSE}
library(plotly)
df <- read.csv("https://raw.githubusercontent.com/plotly/datasets/master/2011_us_ag_exports.csv")
df$hover <- with(df, paste(state, '<br>', "Beef", beef, "Dairy", dairy, "<br>",
                           "Fruits", total.fruits, "Veggies", total.veggies,
                           "<br>", "Wheat", wheat, "Corn", corn))
# give state boundaries a white border
l <- list(color = toRGB("white"), width = 2)
# specify some map projection/options
g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = toRGB('white')
)

p <- plot_geo(df, locationmode = 'USA-states') %>%
  add_trace(
    z = ~total.exports, text = ~hover, locations = ~code,
    color = ~total.exports, colors = 'Purples'
  ) %>%
  colorbar(title = "Millions USD") %>%
  layout(
    title = '2011 US Agriculture Exports by State<br>(Hover for breakdown)',
    geo = g
    
  )
p
```


ggplot to Plotly
```{r message=FALSE,warning=FALSE}
library(plotly)
library(ggplot2)
g=ggplot(mpg,aes(x=displ,y=hwy))+geom_point()

p=ggplotly(g)
p
```


### Bokeh

http://hafen.github.io/rbokeh/#background


```{r message=FALSE,warning=FALSE}
#install.packages("rbokeh")
library(rbokeh)
```

Scatter chart
```{r message=FALSE,warning=FALSE}
p <- figure() %>%
  ly_points(Sepal.Length, Sepal.Width, data = iris,
            color = Species, glyph = Species,
            hover = list(Sepal.Length, Sepal.Width))
p
```
line chart

bar chart

histogram chart

pie chart(not important)

time servies chart


### ggmap

### leaflet

### ggvis

### GoogleVis

### googleCharts


### lattice

histogram:
```{r message=FALSE,warning=FALSE}
# Load the lattice package
library(lattice)
# Create the histogram 
histogram(~ Ozone, data = airquality)
```

Scatter chart:
```{r message=FALSE,warning=FALSE}
# Load the lattice package
library(lattice)
# Create the scatter plot
xyplot(Ozone ~ Solar.R, data = airquality)
```





