# Data Cleaning

Work throught the data like a Ninja

Can you jump,can you nae nae,can you reverse can you filp,split and merge back ,group by and then devide.

Data come in differenct shapes and sizes.

Data cleaning seems to be a dirty job at first ,but its truely the art of data analysis.



## Working with date and time

ISO 8601 standard :YYYY-MM-DD

## working with missing data

## working with string


## Fifty shape of data

tidy data and data wrangler



### dplyr



#### Filter row and select column
```{r eval=FALSE}
mtcars%>%filter(cyl==6)                    # filter cly==6
mtcars%>%filter(cyl==6 & (hp >120|hp<110)) # filter cly==6 and (hp >120 or hp<110)
```

```{r eval=FALSE}
mtcars%>%select(mpg,cyl)                    # select mpg and cyl column
mtcars%>%select(-mpg)                       # select all but exclude mpg
```

#### Summary and group by 

```{r eval=FALSE}
mtcars%>%group_by()%>%summarise(row_number=n(),cyl_number=n_distinct(cyl))   # sum row number and distinct cyl number
mtcars%>%group_by(cyl)%>%summarise(mpg_sum=sum(mpg),mpg_mean=mean(mpg))   # sum mpg and mean mpg for each cyl
```

#### order and transpose

```{r eval=FALSE}
mtcars%>%arrange(desc(cyl))   # order by cyl decreasing
t(mtcars)                     # transpose
```

#### join
```{r eval=FALSE}

left_join(mtcars[c(1:3),],mtcars[c(3:5),],by=c('mpg'='mpg'))   # left join 

full_join(mtcars[c(1:3),],mtcars[c(3:5),],by=c('mpg'='mpg'))   # full join 

inner_join(mtcars[c(1:3),],mtcars[c(3:5),],by=c('mpg'='mpg'))  # inner join 
```


### apply family 

#### apply()

apply to matrix

```{r eval=FALSE}
X <- matrix(rnorm(30), nrow=2, ncol=6) # Construct a 5x6 matrix
apply(X, 2, sum)  # Sum the values of each column with `apply()`  
apply(X, 1, mean)  # mean the values of each row with `apply()` 
```



#### lapply()
The output returned is a list 
```{r eval=FALSE}
A=as.data.frame(matrix(1:9,nrow=3,ncol=3))
B=as.data.frame(matrix(11:19,nrow=3,ncol=3))
C=as.data.frame(matrix(101:109,nrow=3,ncol=3))

MyList <- list(A,B,C)          # Put dataframe A B C to a list 
lapply(MyList,"[", , 2)        # Get each dataframs second col
lapply(MyList,"[", 1, )        # Get each dataframs first row
```


#### sapply()

The sapply() function works like lapply(), but it tries to simplify the output to the most elementary data structure that is possible. And indeed, sapply() is a 'wrapper' function for lapply().

```{r eval=FALSE}
A=as.data.frame(matrix(1:9,nrow=3,ncol=3))
B=as.data.frame(matrix(11:19,nrow=3,ncol=3))
C=as.data.frame(matrix(101:109,nrow=3,ncol=3))

MyList <- list(A,B,C)          # Put dataframe A B C to a list 
sapply(MyList,"[", , 2)        # Get each dataframs second col and put it into a matrix by col
sapply(MyList,"[", 1, )        # Get each dataframs first row  and put it into a matrix by col
```

#### mapply()

The mapply() function stands for 'multivariate apply'. Its purpose is to be able to vectorize arguments to a function that is not usually accepting vectors as arguments.



## tidey data

The Journal of Statistical Software, vol. 59, 2014. by Hadley Wickham.

http://vita.had.co.nz/papers/tidy-data.html

1.Obervation as row
2.Varibale as column
3.One type of observational unit per table

wide dataset

long dataset

tidyr package

gether()  # gather columns into key-value pairs

spread() # spread key-value pairs into columns
separate() # separate one column ino multiple
unite() # unite multiple columns into one















