# Data output

After all the hard work you have done.Now you have  your insignfull ,analytical, story telling result that you want to share with your boss and make him/her think the world will end without you.You need to present it! in many ways.So that they can not aviod you.Make a PPT with excel attchment is not enough.Make them a website.Make them a video or even write them a book.In this Chapter you will get new knowledage on how to show your output.


## R email

```{r eval=FALSE}
library(mailR)
email_name="xxx@gmail.com"
email_password="xxx"

send.mail(from = "xxx@gmail.com",
          to = "xxx@gmail.com",
          subject = "Sent by R ",
          body =
            "
          Hi,
          Sent by R

          Thank you
          
          ",
            authenticate = TRUE,
            attach.files = 'attchemnt.xlsx',
            smtp = list(host.name = "xxx.xxx.com", port = 25,
                        user.name = email_name, passwd = email_password, tls = TRUE)) 

```





## R Presentation
More than a PPT


## R markdown

word



## R notebook

## R bookdown

## R Blogdown

## R mindmap

## R diagramming

With the DiagrammeR package you can create, modify, analyze, and visualize network graph diagrams. The output can be incorporated into RMarkdown documents, integrated with Shiny web apps, converted to other graph formats, or exported as PNG, PDF, or SVG files.

Create a simple diagramme
```{r warning=FALSE,message=FALSE}
#install.packages('DiagrammeR')

library(DiagrammeR)
  
DiagrammeR("graph TB
   A-->B;A-->C;C-->E;B-->D;C-->D;D-->F;E-->F
")  
```  
  
  




