# Data output

After all the hard work you have done.Now you have  your insignfull ,analytical, story telling result that you want to share with your boss and make him/her think the world will end without you.You need to present it! in many ways.So that they can not aviod you.Make a PPT with excel attchment is not enough.Make them a website.Make them a video or even write them a book.In this Chapter you will get new knowledage on how to show your output.



## MS office

### Word
```{r eval=FALSE}
#https://rdrr.io/cran/officer/f/vignettes/word.Rmd
library(officer)
library(dplyr)
#create word
my_doc <- read_docx() 
styles_info(my_doc)

#create a plot 
src <- tempfile(fileext = ".png")
png(filename = src, width = 5, height = 6, units = 'in', res = 300)
barplot(1:10, col = 1:10)
dev.off()

#Add content
my_doc <- my_doc %>% 
  body_add_img(src = src, width = 5, height = 6, style = "centered") %>% 
  body_add_par("Hello world!", style = "Normal") %>% 
  body_add_par("", style = "Normal") %>% # blank paragraph
  body_add_table(iris, style = "table_template")

#output word
print(my_doc, target = "first_example.docx")
```


### PPT
```{r eval=FALSE}
#https://rdrr.io/cran/officer/f/vignettes/powerpoint.Rmd
library(officer)
library(dplyr)
#create PPT
my_pres <- read_pptx() 

#make PPT
my_pres <- my_pres %>% 
  # add slide
  add_slide(layout = "Title and Content", master = "Office Theme")
  ph_with_text(type = "title", str = "A title") %>%
  ph_with_text(type = "ftr", str = "A footer") %>%
  ph_with_text(type = "dt", str = format(Sys.Date())) %>%
  ph_with_text(type = "sldNum", str = "slide 1") %>%
  ph_with_text(str = "Hello world", type = "body")%>%
  # add slide
  add_slide(layout = "Two Content", master = "Office Theme") %>%
  ph_with_text(type = "body", str = "A first text", index = 1) %>%
  ph_with_text(type = "body", str = "A second text", index = 2) %>%
  ph_with_text(type = "title", str = "A title") %>%
  ph_with_text(type = "ftr", str = "Slide footer") %>%
  ph_with_text(type = "dt", str = format(Sys.Date()))

#  layout summary
layout_summary(my_pres)
# output PPT  
print(my_pres, target = "first_example.pptx") %>% 
  invisible()
```







## R email

```{r eval=FALSE}
library(mailR)
email_name="xxx@gmail.com"
email_password="xxx"

send.mail(from = "xxx@gmail.com",
          to = "xxx@gmail.com",
          subject = "Sent by R ",
          body =
            "
          Hi,
          Sent by R

          Thank you
          
          ",
            authenticate = TRUE,
            attach.files = 'attchemnt.xlsx',
            smtp = list(host.name = "xxx.xxx.com", port = 25,
                        user.name = email_name, passwd = email_password, tls = TRUE)) 

```





## R Presentation

## R markdown

## R notebook

## R bookdown

## R Blogdown

## R mindmap
```{r warning=FALSE,message=FALSE}
#install.packages("mindr")
library(mindr)

#example(md2mm)
#mm2md()
example(markmap)
``` 


## R diagramming

With the DiagrammeR package you can create, modify, analyze, and visualize network graph diagrams. The output can be incorporated into RMarkdown documents, integrated with Shiny web apps, converted to other graph formats, or exported as PNG, PDF, or SVG files.

Create a simple diagramme
```{r warning=FALSE,message=FALSE}
#install.packages('DiagrammeR')

library(DiagrammeR)
  
DiagrammeR("graph TB
   A-->B;A-->C;C-->E;B-->D;C-->D;D-->F;E-->F
")  
```  
  
  
## R Shiny App

## Write R funcation
```{r warning=FALSE,message=FALSE}
add1=function(a,b=1){
  c=a+b
  c
}

add1(10)
```  

## Write R package
```{r eval==FALSE}
library(devtools)
library(roxygen2)

# create package cats:
create("cats")
# add function(cat_function.R) in R folder


# create document: 
setwd("./cats")
document()

#install package(cats):
install("cats")
```  




