# Appendix


## The Giants
"If I have seen further, it is by standing on the shoulders of giants" by Isaac Newton.

Hadley Wickham

Joe Cheng

Yihui Xie 


## The Talk

Expressing yourself in R by  Hadley Wickham on 2014 @Stanford Seminar
https://www.youtube.com/watch?v=wki0BqlztCo



All Things R and RStudio
Q&A with J.J. Allaire, Hadley Wickham & Joe Cheng
Moderator: Joseph Rickert
https://www.rstudio.com/resources/videos/all-things-r-and-rstudio/


Finding and Telling Stories with R
by Andrew Flowers from FiveThirtyEight
https://www.rstudio.com/resources/videos/finding-and-telling-stories-with-r/

install.packages('fivethirtyeight')
library(fivethirtyeight)

1.Novelty
2.Outlier
3.Archetype
4.Trend
5.Debunking
6.Forecast


## The Walk

follow the master,work with the master and become the master 


## Appendix to the book

### To Chapter 4 :qplot()[quickly plotting]
#### Scatter plot:
```{r message=FALSE,warning=FALSE}
library(ggplot2)
#Scatter
qplot(displ,hwy,data=mpg)
qplot(displ,hwy,data=mpg,color=drv)# group with color
qplot(displ,hwy,data=mpg,shape=drv)# group with shape
```

#### Scatter and line:
```{r warning=FALSE,message=FALSE}
library(ggplot2)
qplot(displ,hwy,data=mpg,geom=c('point','smooth'))
```

#### Histogram:
```{r message=FALSE,warning=FALSE}
qplot(hwy,data=mpg)
qplot(hwy,data=mpg,fill=drv)# group with color
```


#### facets
```{r message=FALSE,warning=FALSE}
qplot(displ,hwy,data=mpg,facets = .~drv)#facet
qplot(hwy,data=mpg,facets = .~drv,binwidth=2)# facet and binwidth setting
```


