---
title: "My Show 2017"
author: "Tony Duan"
date: "August 6, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Data Pipeline
1. Package
2. Data import
3. Data EDA & visualization
4. Data Cleaning
5. Data Modeling
6. Model Vaildation
7. Model scoring
8. Data output &presentation



## 1.Package

## 2. Data import
1. import from xlsx
2. import from csv
3. import from SAS data
3. import from Database

## data test
```{r,comment=""}
head(mtcars)
```
```{r,comment="",echo=TRUE,eval=FALSE}
tail(mtcars)
```
## data test2
```{r,comment="",echo=TRUE}
library(ggplot2)
ggplot(mtcars, aes(x = mpg, y = disp)) +geom_point()
```

## hello
### first sub heading
#### second sub heading
## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

