--- 
title: "Data Pipeline"
author: "Tony Duan"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: no
github-repo: rstudio/bookdown-demo
description: "This is a Data Pipeline guide ."
---

# Preface

**Contents**
1. Package    
2. Data import
3. Data EDA & visualization
4. Data Cleaning
5. Data Modeling
6. Model Vaildation
7. Model scoring
8. Data output &presentation


**Reference**
www.r-bloggers.com

www.rstudio.com

www.r-project.org

www.wikipedia.org

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

For now, you have to install the development versions of **bookdown** from Github:

```{r eval=FALSE}
devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need to install XeLaTeX.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

<!--chapter:end:index.Rmd-->

# Introduction {#intro}

## History of analytic software
**R** is an implementation of the **S** programming language and created by *Ross Ihaka* and *Robert Gentleman*. at the University of Auckland, New Zealand.R is named partly after the first names of the first two R authors and partly as a play on the name of S. The project was conceived in **1992**, with an initial version released in 1995 and a stable beta version in 2000.

**Python** is created by *Guido van Rossum* in **1991**.Python 3.0 was released on **2008**

**S** is a statistical programming language developed primarily by *John Chambers* at Bell Laboratories in **1975**

Structured Query Language[**SQL**] was initially developed at IBM by *Donald D. Chamberlin* and *Raymond F. Boyce* in **1970**

The development of **SAS** began in **1966** at North Carolina State University by *Anthony Barr* and his student *James Goodnight*(current CEO of SAS)

**C** was originally developed by *Dennis Ritchie* between **1969** and **1973** at Bell Labs

## Install R

R is a **free software** environment for statistical computing and graphics.Download R at CRAN:[www.r-project.org](https://www.r-project.org/)

**CRAN** stand for The Comprehensive R Archive Network. It is a network of ftp and web servers around the world that store identical, up-to-date, versions of code and documentation for R.

**CRAN** is maintained by the efforts of volunteers (the “CRAN team”).That is a group of talent who contribute their time and expertise to make better **Package**

## Install RStudio

RStudio is an **integrated development environment (IDE)** for R. It includes a console, syntax-highlighting editor that supports direct code execution, as well as tools for plotting, history, debugging and workspace management.

Download R Studio:[www.rstudio.com](https://www.rstudio.com/)

## Software navigation

### R

### Rstudio

## Version and location

Check R version run:
```{r}
version
```

update R version run:
```{r eval=FALSE}
install.packages("installr")
library(installr)
updateR()
```

<!--chapter:end:01-intro.Rmd-->

# Package

Part of the reason R has become so popular is the vast array of packages available at the **CRAN**.In the last few years, the number of packages has grown exponentially!

Untill Aug 2017, the CRAN package repository features 11288 available packages.

In order to use a package.we need to first download it and then load the package.

Install a package from CRAN:
```{r eval=FALSE}
install.packages('ggplot2')
```
load a package:
```{r eval=FALSE}
libray(ggplot2)
```

Package on CRAN are been verified and tested by CRAN Team.
Be careful when you need to download Package from other sources.

Install a package from Github**(NOT recommended)**:
```{r eval=FALSE}
install.packages("devtools")
library(devtools)
install_github("hadley/dplyr")
```
Get help on Package: question mark follow by package name
```{r eval=FALSE}
?dplyr
```





**Popluar Package**:

**ggplot2**:ggplot2 is a plotting system for R, based on the grammar of graphics.

**dplyr**:dplyr provides a grammar of data manipulation, providing a consistent set of verbs that solve the most common data manipulation challenges.

**tidyr**:tidyr provides a set of functions that help you get to tidy data.

**readr**:readr provides a fast and friendly way to read rectangular data (like csv, tsv, and fwf).

**tibble**:tibble is a modern re-imaginging of the data frame, keeping what time has proven to be effective, and throwing out what it has not. Tibbles are data.frames that are lazy and surly.

**readxl**:The readxl package makes it easy to get data out of Excel and into R.


<!--chapter:end:02-Package.Rmd-->

# Data import


##Excel

asdfasdf

readxl

XLConnect



##Database 

RJDBC

dplyr

## HTTP

## API & JSON

## Other

SAS


<!--chapter:end:03-Data_import.Rmd-->

# Data EDA

Some _significant_ applications are demonstrated in this chapter.

## visualization



<!--chapter:end:04-Data_EDA.Rmd-->

# Data Cleaning

We have finished a nice book.

<!--chapter:end:05-Data_Cleaning.Rmd-->

# Data Modeling

ASDFASDFA

<!--chapter:end:06-Data_Modeling.Rmd-->

# Model scoring

ASDFASDFA

<!--chapter:end:07-Model_scoring.Rmd-->

# Data output

ASDFASDFA


##presentation

<!--chapter:end:08-Data_output.Rmd-->

