# Package

Part of the reason R has become so popular is the vast array of packages available at the **CRAN**.In the last few years, the number of packages has grown exponentially!

Untill Aug 2017, the CRAN package repository features 11288 available packages.

In order to use a package.we need to first download it and then load the package.

Install a package from CRAN:
```{r eval=FALSE}
install.packages('ggplot2')
```
load a package:
```{r eval=FALSE}
libray(ggplot2)
```

Package on CRAN are been verified and tested by CRAN Team.
Be careful when you need to download Package from other sources.

Install a package from Github**(NOT recommended)**:
```{r eval=FALSE}
install.packages("devtools")
library(devtools)
install_github("hadley/dplyr")
```
Get help on Package: question mark follow by package name
```{r eval=FALSE}
?dplyr
```





**Popluar Package**:

**ggplot2**:ggplot2 is a plotting system for R, based on the grammar of graphics.

**dplyr**:dplyr provides a grammar of data manipulation, providing a consistent set of verbs that solve the most common data manipulation challenges.

**tidyr**:tidyr provides a set of functions that help you get to tidy data.

**readr**:readr provides a fast and friendly way to read rectangular data (like csv, tsv, and fwf).

**tibble**:tibble is a modern re-imaginging of the data frame, keeping what time has proven to be effective, and throwing out what it has not. Tibbles are data.frames that are lazy and surly.

**readxl**:The readxl package makes it easy to get data out of Excel and into R.

