# Data import

## interactive with Operation System[OS]
get current working loaction:
```{r}
getwd()
```

Set current working loaction:
```{r eval=FALSE}
setwd("C:/Users/User/Desktop/Mission/R/R_code/Data_Pipeline/Book")
```

Get computer info:
```{r}
Sys.info()
```

Get file size:
```{r warning=FALSE}
#install.packages('pryr')
library(pryr)
object_size(mtcars)
```

Check how much memory R is using :
```{r warning=FALSE}
mem_used()
memory.size()
```

Check RAM limit :
```{r warning=FALSE}
memory.limit()
```

Show location files:
```{r}
dir(getwd())
```

Create file A B C:
```{r eval=FALSE}
cat("file A\n", file = "A.txt")
cat("file B\n", file = "B.txt")
cat("file C\n", file = "C.txt")
```

Add BBBB...  to A.txt:
```{r eval=FALSE}
file.append("A.txt", rep("B", 10))
```

Open A.txt:
```{r eval=FALSE}
file.show("A.txt")
```

Open A.txt:
```{r eval=FALSE}
file.show("A.txt")
```

Open ebay.com with firefox:
```{r eval=FALSE}
system(paste('"C:/Program Files (x86)/Mozilla Firefox/firefox.exe"',
             '-url www.ebay.com'))
```

Open ebay.com with defalt browser:
```{r eval=FALSE}
browseURL("www.ebay.com")
```

Delete a file with unlink or file.remove():
```{r eval=FALSE}
unlink("C")
file.remove("A", "B")
```

Check a file existence:
```{r eval=FALSE}
dir.exists('test_file')
```

Create a folder :
```{r eval=FALSE}
dir.create('test_file')
```

Delete a folder :
```{r eval=FALSE}
unlink('test_file')
```

Download Files:
```{r eval=FALSE}
download.file()
```

Zip A.txt and B.txt into A_B.zip:
```{r eval=FALSE}
zip("A_B.zip", c("A.txt", "B.txt"))
```

Unzip A_B.zip
```{r eval=FALSE}
unzip("A_B.zip")
```


Untar a file:
```{r eval=FALSE}
untar()
```

Check file info:
```{r message=FALSE, warning=FALSE}
library(dplyr)
dir(getwd())%>%file.info()
```


Shutdown Computer in 10 seconds:
```{r eval=FALSE}
shutdown(wait=10)
```


## Play music
```{r eval=FALSE}
library(tuneR)
File1<- readMP3("Becoming_A_Legend.mp3")
play(File1)
```

## image
```{r eval=FALSE}
library(png)
img<-readPNG("R_logo.png")
```


## CSV
Read csv file:
```{r eval=FALSE}
zipcode <- read.csv("zipcode.csv", header=TRUE)
```


## Excel

asdfasdf

readxl

XLConnect



## Database 

RJDBC

dplyr

## HTTP

## API & JSON

## Other

### SAS
### Matlab 

## Web Crawler

### rvest

### RCurl

### RSelenium




